|

### 2022-12-28 paper.Rmd
Wed Dec 28 10:00:08 CET 2022: update-remote.sh

@@

Regarding the hidden neurons, the dimension of each hidden layer, I used two different strategies: Regular DAE-GP uses the same strategy as described by earlier work (see [@dae-gp_2022_symreg] or [@dae-gp_2020_rtree]), the number of hidden neurons is dynamically set at each generation to the maximum length of all solutions inside the current training population. For pre-trained DAE-GP another strategy had to be used, we use a fixed number of hidden neurons for each run that is set equal to the maximum length of all individuals that are present in the initial pre-training population. I decided to take this aproach instead of using a fixed number of hidden neurons for the fact that it simplifies the adjustment of the parameter for later experiments on different problems. It should nonetheless be mentioned that this strategy does give pre-training on average more hidden neurons per layer resulting in a more complex network (since the pre-training population is much larger than the regular population, the chances for larger individuals inside it are also higher).

@@

```{python include=FALSE}
import json

S = json.load(open("./data/airfoil_FullRun_30gens/MWU-BestFitnessByGen.json", "r", encoding="utf-8"))
statistic_mwu_fitness = S["statistic"]
pval_mwu_fitness = round(S["p-value"], 4)

>>>>

```{bash ipythonRunner}
# Find all *.ipynb files in subdirectories recursively
for file in $(find . -type f -name "*.ipynb"); do
  # Execute the IPython notebook file using the jupyter nbconvert command
  jupyter nbconvert --execute "${file}"
done
```

@@

Regarding the hidden neurons, the dimension of each hidden layer, I used two different strategies: Regular DAE-GP uses the same strategy as described by earlier work (see [@dae-gp_2022_symreg] or [@dae-gp_2020_rtree]), the number of hidden neurons is dynamically set at each generation to the maximum length of all solutions inside the current training population. For pre-trained DAE-GP another strategy had to be used, I used a fixed number of hidden neurons for each run that is set equal to the maximum length of all individuals that are present in the initial pre-training population. I decided to take this aproach instead of using a fixed number of hidden neurons for the fact that it simplifies the adjustment of the parameter for later experiments on different problems. It should nonetheless be mentioned that this strategy does give pre-training on average more hidden neurons per layer resulting in a more complex network (since the pre-training population is much larger than the regular population, the chances for larger individuals inside it are also higher).

@@

```{python load_MWU_ include=FALSE}
from json import load

S = load(open("./data/airfoil_FullRun_30gens/MWU-BestFitnessByGen.json", "r", encoding="utf-8"))
statistic_mwu_fitness = S["statistic"]
pval_mwu_fitness = round(S["p-value"], 4)
print(pval_mwu_fitness)
